---
title: "sunlight"
author: "Maria"
date: "11/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters

### location
So I would like to do plots for my location, i.e. Kunsklippan 14
coordiantes are: 59.330379 lat and 18.048034 lon.

### dates
I would like several dates:

. This year: 2020-01-01 to 2020-12-10
. This and last year: 2019-01-01 to 2020-12-10

### type of radiation

. PAR (W/m²): Photosynthetically active radiation, this spectral region corresponds more or less with the range of light visible to the human eye.
. Global irradiance (W/m²): the total radiation on the surface. Including UV and IR
. CIE UV irradiance (mW/m²): UVB radiation: The major natural source of the vitamin is synthesis of cholecalciferol in the lower layers of skin epidermis through a chemical reaction that is dependent on sun exposure (specifically UVB radiation).

### string

For this year, kungsklippan, Global irradiance

```{r, include=FALSE}
#GET 'https://opendata-download-metanalys.smhi.se/api/category/strang1g/version/1/geotype/point/lon/18.048/lat/59.330/parameter/117/data.json?from=2020-01-01&to=2020-12-10&interval=daily'
```

From 2017 to 2020, Kungsklippan, CIE UV irradiance (mW/m²).

```{r, include=FALSE}
curl GET 'https://opendata-download-metanalys.smhi.se/api/category/strang1g/version/1/geotype/point/lon/18.048/lat/59.330/parameter/116/data.json?from=2017-01-01&to=2020-12-16&interval=daily' > uv2017.json
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

library(ggplot2)
library(streamgraph)
library(gganimate)
library(dplyr)
library("rjson") # library to read JSON
library("jsonlite") # get a list of key/value vectors, convert that to a two column data.frame with stack, rearrange the columns and change the column names (if needed).

  streamgraph(d, "year", "value",  "day", scale="continuous", offset = "zero") %>%
  sg_fill_brewer("PuOr")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

But the glass absorves uv radiation so, it didn't count if you were indoors https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3897598/